### 2021-11-14 response/response.tex

\begin{itemize}
  \item Section IV - first paragraph (page 4):\\
  {\color{Red}
  We modeled the effect caused by impurities in the considered system as a single short-range perturbation potential. Analyzing the electric properties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
  Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
  Furthermore, we assumed that our perturbation potential is formed by a group of randomly distributed impurities under the Edwards impurity model \cite{akkermans10,wackerl20}.
  Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. Then we  approximate the impurity potential into a Gaussian white noise \cite{akkermans10,wackerl20}.
  Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
  Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder. In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
  }
\end{itemize}

@@

\subsubsection*{Comment 5 -
\color{RoyalBlue} If continuous illumination is applied to an electron system, the system will heat indefinitely. The distribution function is stabilized when the electron-electron and electron-phonon scattering mechanisms are included. What are the conditions of validity for eqs. (33-34)? The deviations of the distribution function from its equilibrium result in effects that can significantly overcome the equilibrium contributions, see Dmitriev et al, Phys. Rev. B 80, 165327 (2009). However, to capture these effects, a treatment within Floquet-Drude formalism is insufficient and a complete quantum kinetic equation has to be analyzed. Can the authors argue why their results still present some interest to the community even if they potentially disregard more significant contributions?
}

This is a good, valid question. First, we discuss the validity of the Eq.~[33] and Eq.~[34]. In our analysis, we have derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
In contrast to the MIROs analysis \cite{dmitriev03,dmitriev05,dmitriev09}, we consider the dressed quantum Hall system under the off-resonant condition, where the absorption of photons are avoided. Therefore, we can select the Fermi-Dirac distribution as our particle distribution function on the general expression given in Eq.~[31]
\begin{equation} \tag{5}
  f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1}.
\end{equation}
Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
Then we selected a special scenario where we assumed that the system is under a low-temperature limit or the condition $k_BT \ll \varepsilon_F$.
Since previous theoretical studies \cite{wackerl20,dini16,endo09} on magnetotransport properties of 2DEG quantum Hall systems were derived under this assumption, we selected this condition to provide a better comparison with their outcomes.
In addition, as mentioned in previous experimental studies on SdH oscillations \cite{zudov03,mani02,arapov02} in 2DEG undressed quantum Hall systems with increasing temperature, we can identify the decaying behavior of SdH oscillations.
Therefore, if we need to maintain a good oscillatory behavior we need to work in low temperatures.
Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, it is reasonable to extend our general derivation in given Eq.~[31] into a simple expression through a low-temperature limit. Then we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy. This can be represented by the delta function \cite{endo09}
\begin{equation} \tag{6}
  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
\end{equation}
Applying these adequate conditions, we can simplify our derivation into single expression that can be compared with previous studies \cite{wackerl20,dini16,endo09} on magnetotransport in dressed quantum Hall systems. We have added clarification on the above assumptions in the manuscript.
\begin{itemize}
  \item Section V - second paragraph (page 7):\\
  {\color{Red}
  Since we consider the dressed quantum Hall system under the off-resonant condition, the absorption of photons are avoided. Therefore, we select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
  \begin{equation} \tag{33}
    f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
  \end{equation}
  where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system. Under the low-temperature conditions ($k_BT \ll \varepsilon_F$), we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy. This can be represented by the delta function \cite{endo09}
  \begin{equation} \tag{34}
    - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
  \end{equation}
  }
\end{itemize}

@@

  Moreover, we can identify the $y$-directional current operator component as
  \begin{equation} \tag{D13}
    \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
  \end{equation}
  Using this operator, we can represent the matrix elements of $y$-directional current operator in Floquet mode basis as
  \begin{equation} \tag{D14}
    \left({j}_y \right)_{nm,n'm'} =
    \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
  \end{equation}
  After following the same steps done for the $x$-directional current operator, and recursion relation of the first derivative of Gauss-Hermite functions
  \begin{equation} \tag{D15}
    \begin{aligned}
      \pdv{\chi_{n}({y})}{y} =
      \kappa\left[
      -  \sqrt{\frac{n+1}{2}} \chi_{n+1}({y})
      +  \sqrt{\frac{n}{2}} \chi_{n - 1}({y})
      \right],
    \end{aligned}
  \end{equation}
  we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
  \begin{equation} \tag{D16}
    \begin{aligned}
      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
      \frac{ie\hbar\kappa}{m_e}
      \delta_{k_x,k'_x}
      \left(
      \sqrt{\frac{n}{2}} \delta_{n',n-1}
      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
      \right).
    \end{aligned}
  \end{equation}
  \begin{equation} \tag{D17}
    \begin{aligned}
      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
      \frac{ie \hbar}{m_e l_0}
      \delta_{k_x,k'_x}
      \left(
      \sqrt{\frac{n}{2}} \delta_{n',n-1}
      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
      \right).
    \end{aligned}
  \end{equation}
  }
  \item Section V - second paragraph (page 7):\\
  {\color{Red}
  Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(31) leads to
  \begin{equation} \tag{35}
    \begin{aligned}
      \sigma^{xx}  =
      \frac{e^2l_0^2}{\pi\hbar A}
      \sum_{n}
      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
        }
      \right]
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
        }
      \right],
    \end{aligned}
  \end{equation}
  where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$,
  $\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$, and $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$.
  Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D
  \begin{equation} \tag{36}
    \begin{aligned}
      {\sigma}^{yy} =
      \frac{e^2l_0^2}{\pi\hbar A}
      \sum_{n}
      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
        }
      \right]
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
        }
      \right].
    \end{aligned}
  \end{equation}
  }
\end{itemize}

If we applied an arbitrary directional polarized dressing field, we can derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis. This would change the amplitude of the considering dressing field ($E$) in each direction. Now there will be a new component in parallel to the considering conductivity component and this will modify the time-dependent Hamiltonian given in Eq.~[2]. Then, we need to solve the Schrödinger equation with the modified Hamiltonian to find the new Floquet modes for the new system. These will define the effect on the inverse scattering time matrix components. As mentioned in Ref. \cite{wackerl20} and our work, applied strong dressing field tends to change the quantum state of the considered system and creates novel states called Floquet states. The properties of these states depend on the characteristics of the applied dressing field. Therefore, the polarization method also changes the behavior of the Floquet states. These polarization-dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20,morina15} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields. However, in a dressed quantum Hall system with a $y$-directional linear polarized field, we predict the same longitudinal conductivity behaviors in diagonal components of the conductivity tensor.

@@

We would like to thank the reviewer for his/her insightful comments on our work. To address your comments, we had to add new materials and reorganize our text. As a result, we have been able to considerably improve our discussion on the underlying assumptions and corresponding physical significance of our analysis. We hence believe that both the presentation and scientific content of this manuscript are of a much higher quality than our previous submission. We hope our response and the corresponding changes we incorporated into the manuscript would be sufficient to clarify the issues raised.

\subsubsection*{Comment 1 -
\color{RoyalBlue} The paper is very low on comparison with experiments, for which there is a large amount of data available for the zero radiation case. I would like to see detailed analysis of how Figs 4 and 5 compare with available
experimental data. Without this addition, physical relevance of such
detailed calculations is questionable.
}

We thank the reviewer for pointing out the importance of this fact. To overcome this shortage of discussion we made a detailed analysis of our results against the undressed 2DEG quantum Hall system behavior. We have inserted this discussion into our manuscript under Section VI.

\begin{itemize}
  \item Section VI - third paragraph (page 8):\\
  {\color{Red}
  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig. 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
  As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with a different type of 2DEG have been examined these SdH oscillations against the applied magnetic field amplitude.
  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the considering system.
  Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage. The  change of the gate voltage applied to the system will modify the Fermi level of the system.
  Since the Landau level energy is only dependent on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
  This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature. By comparing these empirical observations with our results given in Fig. 4, we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value. Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased. This will locate to the Fermi level on higher-order Landau levels. As illustrated in Fig. 4, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78} as well. However, in our analysis, we have analytically explained the controllability of these conductivity regions using a dressing field.
  }
\end{itemize}

@@

\subsubsection*{Comment 2 -
\color{RoyalBlue} In the presence of disorder, Anderson localization and topologically protected edge modes are dominant considerations when calculating DC transport coefficients. How are these factors taken into account?
}

We agree with the reviewer that the discussion on the Anderson localization and topologically protected edge modes were missing from the previous manuscript.
We would like to mention to the reviewer that while deriving Eq.~[31], we have assumed that the applied static magnetic field is placed in a lower intensity range where we can neglect several effects known to appear in a 2DEG quantum Hall system. Under this condition, we can neglect the localization in the tails of Landau level peaks, the formation of the edge states, the electron-electron interactions, and the spin splitting as well. As mentioned in the work done by Endo \textit{et al.} \cite{endo09}, under the given magnetic field range, the undressed magnetotransport properties of GaAs/AlGaAs 2DEG quantum Hall system provide an excellent agreement between the experimental observations and theory that was developed by neglecting the above-mentioned effects. We also followed the same theoretical derivation with given assumptions but with an additional dressing field. Our results for the undressed system give a adequate agreement with the results from Ref. \cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks. We have added this clarification in the manuscript.

\begin{itemize}
  \item Section I - sixth paragraph (page 2):\\
  {\color{Red}
  It is important to note that, in this analysis, we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions can be neglected. The use of this assumption can also be found in the study done by Endo \textit{et al.} \cite{endo09}.
  }
  \item Section VIII - first paragraph (page 10):\\
  {\color{Red}
  We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within an order where we can neglect effects of the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions.
  }
\end{itemize}

@@

\subsubsection*{Comment 3 -
\color{RoyalBlue} Can the authors reproduce the quantized Hall conductance of filled Landau levels in the presence of disorder? Please discuss.
}

For analyzing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}. The Floquet-Drude conductivity formula was only developed for the diagonal components of the conductivity tensor of the considering system. In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analyzed the dressing field effect on two diagonal components of the conductivity tensor through the Floquet-Drude conductivity formula. Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these types of behaviors of dressed 2DEG quantum Hall systems. However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behavior of off-diagonal components of the conductivity tensor. As mentioned in Ref. \cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly match with the experiment observations
\begin{equation} \tag{1}
  \dv{\widetilde{\sigma}^{xy}(X_F,I)}{B} \approx
    \pi\mu \frac{\hbar \omega_0}{\varepsilon_F} [\widetilde{\sigma}^{xx}(X_F,I)]^2.
\end{equation}
By examining the connection between longitudinal and transverse conductivities in the 2DEG quantum Hall system, we can expect the same Hall conductivity behavior in a dressed quantum Hall system. However, using the dressing field we can squeeze the conductivity peaks on Landau levels. This will squeeze the region of longitudinal conductivity peaks placed near the Landau levels. This will imply sudden Hall conductivity transitions between one plateau to another near a Landau level. As empirical observation shown in Refs.  \cite{klitzing80,gusynin06}, we can predict a staircase behavior for quantum Hall conductivity agaist the gate voltage. With a external dressing field we will be able to get rapid transitions than the undressed system. However, to derive an analytical expression for the quantum Hall conductivity through Floquet-Drude conductivity needs to be reformulated from the begin and it will be the subject of our future study.

@@

\subsubsection*{Comment 4 -
\color{RoyalBlue} The way some previous works are cited is disappointing. Example from page 8: “Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.” This is not informative. Where, specifically, did results from earlier works fall short of reality, which have been better addressed in this work?
}

We would like to thank the reviewer for pointing out the deficiencies in our manuscript and we have considered your recommendations seriously. We made the following changes in language and presentation to improve the clarity of our manuscript.

### 2021-11-14 response/response.tex

\begin{itemize}
  \item Section VIII (page 8):\\
  {\color{Red}
  Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results do not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref. \cite{endo09}. This is due to the fact that the authors of Ref. \cite{dini16} has been used the conventinal expression of longitudinal conductivity from Refs. \cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
  However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.
  }
  \item Section III - first paragraph (page 3):\\
  {\color{Red}
  In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field. Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
  }
  \item Section I - fifth paragraph (page 2):\\
  {\color{Red}
  The authors of Ref. \cite{dini16} used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
  }
  \item Section IV - third paragraph (page 5):\\
  {\color{Red}
  In the study presented in Ref. \cite{endo09}, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
  }
\end{itemize}
